Title

### 2013-01-29 inc/hardware/column.tex
generalized hardware folder

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube,'' having six 4.5 in ConFlat ports on a cube, with eight 1.33 in ports on the corners.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''

>>>>

Kimball's line of Multi-CF hardware has been especially useful in building the prototype column.
The main chamber is a 4.5 in ``spherical cube,'' having six 4.5 in ConFlat ports on a cube, with eight 1.33 in ports on the corners.
All ports on Multi-CF hardware also contain a set of grooves, designed as mounting points for a system of erector-set-like equipment called ``eV Parts.''
This system is used to mount the accelerator anode and the the deflector plates which are both to be described later.
